
# Packages
```{r}
library(tidyverse)
library(rstan)
library(bridgesampling)
```


# BAYESIAN MODEL AVERAGING

# 1) Quadratic model

## 1.1) Stan code
Define the Stan code for the quadratic model
```{r}
stan_model_QD <- "// The input data is a vector 'y' of length 'N'.
data {
  int<lower=0> N;
  real<lower=0> pN; // Fertilizer price
  real<lower=0> pC; // Corn price
  vector[N] y;
  vector[N] x;
}

transformed data {
   real<lower=0> PR;
   PR = pN/pC;
}

// The parameters accepted by the model. Our model
// accepts two parameters 'mu' and 'sigma'.
parameters {
  real<lower=0> b0;
  real<lower=0> b1;
  real<lower=0> b2;
  real<lower=0> sigma;
}

// The model to be estimated. We model the output
// 'y' to be normally distributed with mean 'mu'
// and standard deviation 'sigma'.
model {
  // Define the mean
  // Define the likelihood
  target += normal_lpdf(y | b0 + (b1 * x) - (b2 * x^2), sigma);
  // Define the priors
  target += gamma_lpdf(b0 | 2.93, 0.00049);
  target += gamma_lpdf(b1 | 2.25, 0.05);
  target += gamma_lpdf(b2 | 0.75, 4);
  target += student_t_lpdf(sigma | 3, 0, 5);

}

generated quantities {
// Define the economic optimum N rate
real<lower=0> EONR;
// Calculate the economic optimum N rate
EONR = fmax((b1-PR)/(2*b2),0);
}

"

```


## 1.2) Create a function to fit the model
```{r}
bayes_model_QD <- function(x,y,pN,pC,
                        param_saved = c("b0", "b1",
                                        "b2", "EONR",
                                        "sigma"
                                        ),
                        chains = 4, iter = 4000, warmup = 2000,
                        cores = 1, apt_del = 0.9, thin = 5, 
                        seed = 79
                        ){
  
  df.list <- list(x = x,
               y = y,
               pN=pN,
               pC=pC,
               N = length(y))
  
  stan(model_code = stan_model_QD,
       data = df.list,
       chains = chains,
       iter = iter,
       warmup = warmup,
       cores = cores,
       control=list(adapt_delta= apt_del),
       thin = thin,
       seed = seed,
       pars = param_saved
       )
  
}
```

## 1.3) Fit the model
```{r}
bay.mod_QD <- bayes_model_QD(
      x = df$x,
      y = df$y,
      # Nitrogen price
      pN = 0.789,
      # Corn price
      pC = 0.154
    )

# Convergence checking
summary(bay.mod_QD)
```



# 2) Quadratic Plateau
## 2.1) Stan code
Define the Stan code for the quadratic plateau model

```{r}
stan_model_QP <- "// The input data is a vector 'y' of length 'N'.
data {
  int<lower=0> N;
  real<lower=0> pN; // Fertilizer price
  real<lower=0> pC; // Corn price
  vector[N] y;
  vector[N] x;
}

transformed data {
   real<lower=0> PR;
   PR = pN/pC;
}

// The parameters accepted by the model. Our model
// accepts two parameters 'mu' and 'sigma'.
parameters {
  real<lower=0> b0;
  real<lower=0> b1;
  real<lower=0> b2;
  real<lower=0> sigma;
}

// The model to be estimated. We model the output
// 'y' to be normally distributed with mean 'mu'
// and standard deviation 'sigma'.
model {
  vector[N] mu;
  // Define the mean
  for(i in 1:N) {
  if (x[i] < b1 / (2 * b2)) {
      mu[i] = b0 + b1 * x[i] - b2 * x[i]^2;
    } else {
      real xp = b1 / (2 * b2);
      mu[i] = b0 + b1 * xp - b2 * xp^2;
    }
   }
  
  // Define the likelihood
  target += normal_lpdf(y | mu, sigma);
  // Define the priors
  target += gamma_lpdf(b0 | 2.93, 0.00049);
  target += gamma_lpdf(b1 | 2.25, 0.05);
  target += gamma_lpdf(b2 | 0.75, 4);
  target += student_t_lpdf(sigma | 3, 0, 5);
}

generated quantities {
// Define the economic optimum N rate
real<lower=0> EONR;
// Calculate the economic optimum N rate
EONR = fmax((b1-PR)/(2*b2),0);
}

"

```

## 2.2) Create a function to fit the model
```{r}
bayes_model_QP <- function(x,y,pN,pC,
                        param_saved = c("b0", "b1",
                                        "b2", "EONR",
                                        "sigma"
                                        ),
                        chains = 4, iter = 4000, warmup = 2000,
                        cores = 1, apt_del = 0.9, thin = 5, 
                        seed = 79
                        ){
  
  df.list <- list(x = x,
               y = y,
               pN=pN,
               pC=pC,
               N = length(y))
  
  stan(model_code = stan_model_QP,
       data = df.list,
       chains = chains,
       iter = iter,
       warmup = warmup,
       cores = cores,
       control=list(adapt_delta= apt_del),
       thin = thin,
       seed = seed,
       pars = param_saved
       )
  
}
```

## 2.3) Fit the model
```{r}
bay.mod_QP <- bayes_model_QP(
      x = df$x,
      y = df$y,
      # Nitrogen price
      pN = 0.789,
      # Corn price
      pC = 0.154)

# Convergence checking
summary(bay.mod_QP)
```



# 3) Linear Plateau model
## 3.1) Stan code
Define the Stan code for the linear plateau model
```{r}
stan_model_LinPl <- "// The input data is a vector 'y' of length 'N'.
data {
  int<lower=0> N;
  vector[N] y;
  vector[N] x;
}

// The parameters accepted by the model. Our model
// accepts two parameters 'mu' and 'sigma'.
parameters {
  real<lower=0> b0;
  real<lower=0> b1;
  real<lower=0> EONR; // The EONR in this model corresponds to the break point
  real<lower=0> sigma;
}

// The model to be estimated. We model the output
// 'y' to be normally distributed with mean 'mu'
// and standard deviation 'sigma'.
model {

vector[N] mu;
  // Define the mean
  for(i in 1:N) {
  if (x[i] < EONR) {
      mu[i] = b0 + b1 * x[i];
    } else {
      mu[i] = b0 + b1 * EONR;
    }
  }
  

  // Define the likelihood
  target += normal_lpdf(y | mu, sigma);
  // Define the priors
  target += gamma_lpdf(b0 | 2.93, 0.00049);
  target += gamma_lpdf(b1 | 2.25, 0.05);
  target += gamma_lpdf(EONR | 1.55, 0.0103);
  target += student_t_lpdf(sigma | 3, 0, 5);
}

"

```


## 3.2) Create a function to fit the model
```{r}
bayes_model_LinPl <- function(x,y,
                        param_saved = c("b0", "b1",
                                        "EONR",
                                        "sigma"
                                        ),
                        chains = 4, iter = 4000, warmup = 2000,
                        cores = 1, apt_del = 0.9, thin = 5, 
                        seed = 79
                        ){
  
  df.list <- list(x = x,
               y = y,
               N = length(y))
  
  stan(model_code = stan_model_LinPl,
       data = df.list,
       chains = chains,
       iter = iter,
       warmup = warmup,
       cores = cores,
       control=list(adapt_delta= apt_del),
       thin = thin,
       seed = seed,
       pars = param_saved
       )
  
}
```

## 3.3) Fit the model
```{r}
bay.mod_LP <- bayes_model_LinPl(
      x = df$x,
      y = df$y)

# Convergence checking
summary(bay.mod_LP)
```


# 4) Mitscherlich model

## 4.1) Stan code
Define the Stan code for the Mitscherlich model
```{r}
stan_model_MIT <- "// The input data is a vector 'y' of length 'N'.
data {
  int<lower=0> N;
  real<lower=0> pN; // Fertilizer price
  real<lower=0> pC; // Corn price
  vector[N] y;
  vector[N] x;
}

// The parameters accepted by the model. Our model
// accepts two parameters 'mu' and 'sigma'.
parameters {
  real<lower=0> b0;
  real<lower=0> b1;
  real<lower=0> b2;
  real<lower=0> sigma;
}

// The model to be estimated. We model the output
// 'y' to be normally distributed with mean 'mu'
// and standard deviation 'sigma'.
model {
  // Define the mean
  // Define the likelihood
  target += normal_lpdf(y |  b0+(b1-b0)*exp(-b2*x), sigma);
  // Define the priors
  target += gamma_lpdf(b0 | 4,  0.00033);
  target += gamma_lpdf(b1 | 2.25, 0.000375);
  target += gamma_lpdf(b2 | 0.444, 44.444);
  target += student_t_lpdf(sigma | 3, 0, 5);
}

generated quantities {
// Define the economic optimum N rate
real<lower=0> EONR;
// Calculate the economic optimum N rate
EONR = fmax(-log(-pN/(pC*(b1-b0)*b2))/b2,0);
}

"

```


## 4.2) Create a function to fit the model
```{r}
bayes_model_MIT <- function(x,y,pN,pC,
                        param_saved = c("b0", "b1",
                                        "b2", "EONR",
                                        "sigma"
                                        ),
                        chains = 4, iter = 4000, warmup = 2000,
                        cores = 1, apt_del = 0.9, thin = 5, 
                        seed = 79
                        ){
  
  df.list <- list(x = x,
               y = y,
               pN=pN,
               pC=pC,
               N = length(y))
  
  stan(model_code = stan_model_MIT,
       data = df.list,
       chains = chains,
       iter = iter,
       warmup = warmup,
       cores = cores,
       control=list(adapt_delta= apt_del),
       thin = thin,
       seed = seed,
       pars = param_saved
       )
  
}

```


## 4.3) Fit the model
```{r}
bay.mod_MIT <- bayes_model_MIT(x = df$x,
                               y = df$y,
                               # Nitrogen price
                               pN=0.789,
                               # Corn price
                               pC=0.154
                               )

# Convergence checking
summary(bay.mod_MIT)
```


# 5) Model Probability
## 5.1) Computes log marginal likelihood via bridge sampling
```{r}
QD_marglog <- bridgesampling::bridge_sampler(bay.mod_QD,silent = TRUE)
QP_marglog <- bridgesampling::bridge_sampler(bay.mod_QP,silent = TRUE)
LP_marglog <- bridgesampling::bridge_sampler(bay.mod_LP,silent = TRUE)
MIT_marglog <- bridgesampling::bridge_sampler(bay.mod_MIT,silent = TRUE)
```

## 5.2) Compute posterior model probabilities from marginal likelihoods.
```{r}
m_prob <- bridgesampling::post_prob(QD_marglog,QP_marglog,
                                    LP_marglog,MIT_marglog,
                                    # Define equal prior model probability
                                    prior_prob = c(.25,.25,
                                                   .25,.25))

m_prob
```




